Bayesian Hyper-Heuristics

### 2023-02-04 article/sections/08-results.tex
🚧 (article): Save point

>>>>

\begin{table}[htb]
	\centering
	\caption{Empirical results showing normalised average rank and statistics for the top six low-level heuristics and three heuristic pool variants of the \acs{BHH} baseline configuration, across multiple datasets, for all independent runs and epochs.}
	\label{tab:results:standalone:metrics:rank_a}%
	\par\bigskip
	\resizebox{\textwidth}{!}{
		\begin{tabular}{r|ccc|c|c|c|}
			                              & \multicolumn{6}{c|}{\textbf{BHH vs. Low-Level Heuristics - Average Rank (Part A)}}                                                                                                                                                                                                                                                                                                   \\
			\midrule
			\textbf{dataset}              & \textbf{adagrad}                                                                   & \textbf{adam}                                           & \textbf{rmsprop}                                        & \textbf{bhh\_gd}                                        & \textbf{nag}                                            & \textbf{bhh\_all}                                       \\
			\midrule
			\textbf{abalone}              & \cellcolor[rgb]{ .388,  .745,  .482}2,2215 ($\pm$1,591)                            & \cellcolor[rgb]{ .416,  .753,  .482}2,3989 ($\pm$1,887) & \cellcolor[rgb]{ .78,  .859,  .502}4,6172 ($\pm$2,65)   & \cellcolor[rgb]{ .796,  .863,  .506}4,7032 ($\pm$2,108) & \cellcolor[rgb]{ .725,  .839,  .498}4,2731 ($\pm$1,542) & \cellcolor[rgb]{ 1,  .922,  .518}5,9376 ($\pm$2,399)    \\
			\textbf{air\_quality}         & \cellcolor[rgb]{ .427,  .757,  .482}3,6409 ($\pm$2,259)                            & \cellcolor[rgb]{ .804,  .863,  .506}5,4312 ($\pm$2,62)  & \cellcolor[rgb]{ .388,  .745,  .482}3,4452 ($\pm$2,57)  & \cellcolor[rgb]{ .729,  .843,  .502}5,0817 ($\pm$2,762) & \cellcolor[rgb]{ .467,  .765,  .486}3,8194 ($\pm$2,229) & \cellcolor[rgb]{ 1,  .894,  .514}6,686 ($\pm$3,061)     \\
			\textbf{bank}                 & \cellcolor[rgb]{ .455,  .765,  .486}2,5495 ($\pm$1,598)                            & \cellcolor[rgb]{ .388,  .745,  .482}2,0796 ($\pm$1,587) & \cellcolor[rgb]{ .588,  .8,  .49}3,4645 ($\pm$2,209)    & \cellcolor[rgb]{ .8,  .863,  .506}4,8828 ($\pm$1,702)   & \cellcolor[rgb]{ .71,  .835,  .498}4,2871 ($\pm$1,732)  & \cellcolor[rgb]{ 1,  .922,  .518}6,2419 ($\pm$2,157)    \\
			\textbf{bike}                 & \cellcolor[rgb]{ .388,  .745,  .482}1,7204 ($\pm$1,384)                            & \cellcolor[rgb]{ .643,  .816,  .494}3,6925 ($\pm$4,004) & \cellcolor[rgb]{ .973,  .914,  .514}6,2624 ($\pm$4,58)  & \cellcolor[rgb]{ .663,  .824,  .498}3,8441 ($\pm$1,398) & \cellcolor[rgb]{ 1,  .922,  .518}6,4516 ($\pm$1,02)     & \cellcolor[rgb]{ .71,  .835,  .498}4,2151 ($\pm$1,361)  \\
			\textbf{car}                  & \cellcolor[rgb]{ .702,  .835,  .498}4,7634 ($\pm$0,938)                            & \cellcolor[rgb]{ .388,  .745,  .482}1,6226 ($\pm$1,405) & \cellcolor[rgb]{ .455,  .765,  .486}2,3269 ($\pm$1,409) & \cellcolor[rgb]{ .561,  .792,  .49}3,3473 ($\pm$1,35)   & \cellcolor[rgb]{ .831,  .871,  .506}6,0785 ($\pm$0,799) & \cellcolor[rgb]{ .58,  .8,  .49}3,5624 ($\pm$1,315)     \\
			\textbf{diabetic}             & \cellcolor[rgb]{ .506,  .776,  .486}2,7796 ($\pm$1,659)                            & \cellcolor[rgb]{ 1,  .886,  .514}7,1484 ($\pm$2,227)    & \cellcolor[rgb]{ 1,  .922,  .518}6,7376 ($\pm$2,577)    & \cellcolor[rgb]{ .812,  .867,  .506}5,2269 ($\pm$2,186) & \cellcolor[rgb]{ .388,  .745,  .482}1,8118 ($\pm$1,413) & \cellcolor[rgb]{ .988,  .69,  .475}9,3968 ($\pm$3,022)  \\
			\textbf{fish\_toxicity}       & \cellcolor[rgb]{ .533,  .784,  .49}4,2645 ($\pm$2,614)                             & \cellcolor[rgb]{ .388,  .745,  .482}3,6022 ($\pm$2,445) & \cellcolor[rgb]{ .388,  .745,  .482}3,5946 ($\pm$2,329) & \cellcolor[rgb]{ .784,  .859,  .502}5,4118 ($\pm$2,665) & \cellcolor[rgb]{ .89,  .89,  .51}5,8914 ($\pm$2,629)    & \cellcolor[rgb]{ .875,  .886,  .51}5,829 ($\pm$2,856)   \\
			\textbf{forest\_fires}        & \cellcolor[rgb]{ .769,  .855,  .502}5,1559 ($\pm$2,922)                            & \cellcolor[rgb]{ .388,  .745,  .482}4,2688 ($\pm$2,984) & \cellcolor[rgb]{ .718,  .839,  .498}5,0355 ($\pm$3,143) & \cellcolor[rgb]{ .569,  .796,  .49}4,6935 ($\pm$2,759)  & \cellcolor[rgb]{ 1,  .922,  .518}5,6882 ($\pm$2,215)    & \cellcolor[rgb]{ .91,  .894,  .51}5,4839 ($\pm$3,107)   \\
			\textbf{housing}              & \cellcolor[rgb]{ .404,  .749,  .482}3,4484 ($\pm$2,025)                            & \cellcolor[rgb]{ .388,  .745,  .482}3,3344 ($\pm$1,819) & \cellcolor[rgb]{ .439,  .757,  .482}3,6946 ($\pm$2,166) & \cellcolor[rgb]{ .553,  .792,  .49}4,4742 ($\pm$2,312)  & \cellcolor[rgb]{ .584,  .8,  .49}4,6839 ($\pm$2,658)    & \cellcolor[rgb]{ .537,  .788,  .49}4,3763 ($\pm$2,438)  \\
			\textbf{iris}                 & \cellcolor[rgb]{ .965,  .91,  .514}6,3946 ($\pm$1,6)                               & \cellcolor[rgb]{ .525,  .784,  .49}3,5839 ($\pm$2,511)  & \cellcolor[rgb]{ .388,  .745,  .482}2,6968 ($\pm$1,912) & \cellcolor[rgb]{ .706,  .835,  .498}4,7473 ($\pm$2,275) & \cellcolor[rgb]{ .522,  .78,  .486}3,5548 ($\pm$2,125)  & \cellcolor[rgb]{ .78,  .859,  .502}5,2204 ($\pm$3,041)  \\
			\textbf{mushroom}             & \cellcolor[rgb]{ .71,  .835,  .498}4,4656 ($\pm$1,053)                             & \cellcolor[rgb]{ .388,  .745,  .482}2,1344 ($\pm$1,883) & \cellcolor[rgb]{ .431,  .757,  .482}2,4656 ($\pm$1,359) & \cellcolor[rgb]{ .569,  .796,  .49}3,4484 ($\pm$1,602)  & \cellcolor[rgb]{ .969,  .91,  .514}6,3323 ($\pm$0,891)  & \cellcolor[rgb]{ .6,  .804,  .494}3,6688 ($\pm$2,469)   \\
			\textbf{parkinsons}           & \cellcolor[rgb]{ .412,  .749,  .482}2,4677 ($\pm$1,497)                            & \cellcolor[rgb]{ .388,  .745,  .482}2,2333 ($\pm$1,742) & \cellcolor[rgb]{ .541,  .788,  .49}3,5656 ($\pm$2,492)  & \cellcolor[rgb]{ .655,  .82,  .494}4,572 ($\pm$1,934)   & \cellcolor[rgb]{ 1,  .922,  .518}7,5355 ($\pm$1,44)     & \cellcolor[rgb]{ .635,  .816,  .494}4,3839 ($\pm$1,861) \\
			\textbf{student\_performance} & \cellcolor[rgb]{ .388,  .745,  .482}2,5634 ($\pm$1,912)                            & \cellcolor[rgb]{ .98,  .506,  .439}11,3978 ($\pm$2,178) & \cellcolor[rgb]{ .973,  .412,  .42}12,4312 ($\pm$1,34)  & \cellcolor[rgb]{ .843,  .875,  .506}5,6624 ($\pm$3,57)  & \cellcolor[rgb]{ .478,  .769,  .486}3,1935 ($\pm$2,12)  & \cellcolor[rgb]{ .875,  .882,  .51}5,8634 ($\pm$3,159)  \\
			\textbf{wine\_quality}        & \cellcolor[rgb]{ .569,  .796,  .49}3,2806 ($\pm$1,931)                             & \cellcolor[rgb]{ .388,  .745,  .482}2,1118 ($\pm$1,666) & \cellcolor[rgb]{ .624,  .812,  .494}3,6301 ($\pm$1,731) & \cellcolor[rgb]{ .808,  .863,  .506}4,7882 ($\pm$2,105) & \cellcolor[rgb]{ .706,  .835,  .498}4,1505 ($\pm$1,916) & \cellcolor[rgb]{ .871,  .882,  .51}5,1925 ($\pm$1,951)  \\
			\midrule
			\textbf{avg rank}             & \cellcolor[rgb]{ .388,  .745,  .482}3,5512 ($\pm$2,25)                             & \cellcolor[rgb]{ .471,  .769,  .486}3,9314 ($\pm$3,423) & \cellcolor[rgb]{ .616,  .808,  .494}4,5691 ($\pm$3,517) & \cellcolor[rgb]{ .631,  .812,  .494}4,6346 ($\pm$2,364) & \cellcolor[rgb]{ .675,  .827,  .498}4,8394 ($\pm$2,384) & \cellcolor[rgb]{ .808,  .867,  .506}5,4327 ($\pm$2,9)   \\
			\midrule
			\textbf{normalised avg rank}  & \cellcolor[rgb]{ .388,  .745,  .482}1                                              & \cellcolor[rgb]{ .49,  .773,  .486}2                    & \cellcolor[rgb]{ .592,  .804,  .494}3                   & \cellcolor[rgb]{ .694,  .831,  .498}4                   & \cellcolor[rgb]{ .796,  .863,  .506}5                   & \cellcolor[rgb]{ .898,  .89,  .51}6                     \\
			\cmidrule{5-5}\cmidrule{7-7}\end{tabular}%
	}
\end{table}%

\begin{table}[htb]
	\centering
	\caption{Empirical results showing normalised average rank and statistics for the bottom six low-level heuristics and three heuristic pool variants of the \acs{BHH} baseline configuration, across multiple datasets, for all independent runs and epochs.}
	\label{tab:results:standalone:metrics:rank_b}%
	\par\bigskip
	\resizebox{\textwidth}{!}{
		\begin{tabular}{r|c|c|ccccc|}
			                              & \multicolumn{7}{c}{\textbf{BHH vs. Low-Level Heuristics - Average Rank (Part B)}}                                                                                                                                                                                                                                                                                                                                                                  \\
			\midrule
			\textbf{dataset}              & \textbf{adadelta}                                                                 & \textbf{bhh\_mh}                                        & \textbf{ga}                                              & \textbf{pso}                                             & \textbf{sgd}                                             & \textbf{momentum}                                        & \textbf{de}                                              \\
			\midrule
			\textbf{abalone}              & \cellcolor[rgb]{ .894,  .89,  .51}5,3129 ($\pm$1,478)                             & \cellcolor[rgb]{ .992,  .749,  .486}8,1882 ($\pm$1,195) & \cellcolor[rgb]{ .98,  .525,  .443}11,1108 ($\pm$1,102)  & \cellcolor[rgb]{ .98,  .514,  .439}11,2559 ($\pm$1,826)  & \cellcolor[rgb]{ .992,  .718,  .478}8,628 ($\pm$1,019)   & \cellcolor[rgb]{ .984,  .624,  .463}9,8151 ($\pm$1,16)   & \cellcolor[rgb]{ .973,  .412,  .42}12,5376 ($\pm$1,329)  \\
			\textbf{air\_quality}         & \cellcolor[rgb]{ .765,  .851,  .502}5,2441 ($\pm$3,162)                           & \cellcolor[rgb]{ 1,  .922,  .518}6,357 ($\pm$2,303)     & \cellcolor[rgb]{ .996,  .784,  .494}7,8204 ($\pm$2,265)  & \cellcolor[rgb]{ .984,  .588,  .455}9,9151 ($\pm$2,288)  & \cellcolor[rgb]{ .98,  .518,  .443}10,6613 ($\pm$1,606)  & \cellcolor[rgb]{ .973,  .412,  .42}11,7559 ($\pm$1,473)  & \cellcolor[rgb]{ .976,  .471,  .431}11,1419 ($\pm$2,236) \\
			\textbf{bank}                 & \cellcolor[rgb]{ .914,  .894,  .51}5,672 ($\pm$1,241)                             & \cellcolor[rgb]{ .988,  .639,  .463}9,7495 ($\pm$1,048) & \cellcolor[rgb]{ .98,  .537,  .447}10,9817 ($\pm$1,216)  & \cellcolor[rgb]{ .976,  .467,  .431}11,8376 ($\pm$1,464) & \cellcolor[rgb]{ .992,  .757,  .486}8,2774 ($\pm$1,03)   & \cellcolor[rgb]{ .992,  .741,  .486}8,4774 ($\pm$1,068)  & \cellcolor[rgb]{ .973,  .412,  .42}12,4989 ($\pm$1,224)  \\
			\textbf{bike}                 & \cellcolor[rgb]{ .859,  .878,  .506}5,3602 ($\pm$1,155)                           & \cellcolor[rgb]{ .996,  .843,  .506}7,4108 ($\pm$1,008) & \cellcolor[rgb]{ .988,  .686,  .475}9,2269 ($\pm$1,183)  & \cellcolor[rgb]{ .988,  .682,  .475}9,3086 ($\pm$1,761)  & \cellcolor[rgb]{ .984,  .596,  .455}10,3355 ($\pm$1,419) & \cellcolor[rgb]{ .984,  .561,  .451}10,7086 ($\pm$1,423) & \cellcolor[rgb]{ .973,  .412,  .42}12,4634 ($\pm$1,465)  \\
			\textbf{car}                  & \cellcolor[rgb]{ 1,  .922,  .518}7,7344 ($\pm$1,746)                              & \cellcolor[rgb]{ .996,  .8,  .498}8,8505 ($\pm$1,413)   & \cellcolor[rgb]{ .984,  .592,  .455}10,7763 ($\pm$1,471) & \cellcolor[rgb]{ 1,  .855,  .506}8,3613 ($\pm$1,622)     & \cellcolor[rgb]{ .988,  .651,  .467}10,2452 ($\pm$1,447) & \cellcolor[rgb]{ .984,  .576,  .451}10,9226 ($\pm$1,349) & \cellcolor[rgb]{ .973,  .412,  .42}12,4086 ($\pm$1,492)  \\
			\textbf{diabetic}             & \cellcolor[rgb]{ .494,  .773,  .486}2,6753 ($\pm$1,629)                           & \cellcolor[rgb]{ .992,  .765,  .49}8,557 ($\pm$1,17)    & \cellcolor[rgb]{ .98,  .529,  .443}11,2011 ($\pm$1,413)  & \cellcolor[rgb]{ .984,  .573,  .451}10,7022 ($\pm$1,067) & \cellcolor[rgb]{ .898,  .89,  .51}5,9215 ($\pm$1,542)    & \cellcolor[rgb]{ .949,  .906,  .514}6,3355 ($\pm$1,612)  & \cellcolor[rgb]{ .973,  .412,  .42}12,5065 ($\pm$1,242)  \\
			\textbf{fish\_toxicity}       & \cellcolor[rgb]{ .996,  .788,  .494}7,914 ($\pm$3,429)                            & \cellcolor[rgb]{ 1,  .922,  .518}6,3849 ($\pm$2,944)    & \cellcolor[rgb]{ 1,  .894,  .514}6,7043 ($\pm$2,82)      & \cellcolor[rgb]{ .996,  .82,  .498}7,5731 ($\pm$2,982)   & \cellcolor[rgb]{ .976,  .471,  .431}11,5785 ($\pm$1,459) & \cellcolor[rgb]{ .973,  .412,  .42}12,2301 ($\pm$1,382)  & \cellcolor[rgb]{ .984,  .608,  .459}10,0215 ($\pm$2,358) \\
			\textbf{forest\_fires}        & \cellcolor[rgb]{ 1,  .859,  .506}6,5161 ($\pm$3,082)                              & \cellcolor[rgb]{ .898,  .89,  .51}5,4591 ($\pm$2,668)   & \cellcolor[rgb]{ .996,  .796,  .494}7,3667 ($\pm$2,37)   & \cellcolor[rgb]{ 1,  .863,  .51}6,4796 ($\pm$3,354)      & \cellcolor[rgb]{ .98,  .529,  .443}10,8129 ($\pm$1,207)  & \cellcolor[rgb]{ .976,  .463,  .431}11,7065 ($\pm$1,325) & \cellcolor[rgb]{ .973,  .412,  .42}12,3333 ($\pm$1,923)  \\
			\textbf{housing}              & \cellcolor[rgb]{ 1,  .918,  .518}7,5903 ($\pm$2,748)                              & \cellcolor[rgb]{ 1,  .922,  .518}7,5441 ($\pm$1,736)    & \cellcolor[rgb]{ 1,  .878,  .51}7,8839 ($\pm$2,099)      & \cellcolor[rgb]{ .984,  .608,  .459}9,9409 ($\pm$2,317)  & \cellcolor[rgb]{ .973,  .412,  .42}11,4075 ($\pm$1,528)  & \cellcolor[rgb]{ .976,  .431,  .424}11,2731 ($\pm$1,506) & \cellcolor[rgb]{ .976,  .42,  .424}11,3484 ($\pm$2,096)  \\
			\textbf{iris}                 & \cellcolor[rgb]{ .973,  .412,  .42}11,3527 ($\pm$1,779)                           & \cellcolor[rgb]{ 1,  .922,  .518}6,6075 ($\pm$2,555)    & \cellcolor[rgb]{ .992,  .749,  .486}8,2473 ($\pm$1,765)  & \cellcolor[rgb]{ .992,  .745,  .486}8,2731 ($\pm$4,384)  & \cellcolor[rgb]{ .98,  .518,  .443}10,3796 ($\pm$1,294)  & \cellcolor[rgb]{ .976,  .447,  .427}11,0548 ($\pm$1,409) & \cellcolor[rgb]{ .988,  .678,  .471}8,8871 ($\pm$3,251)  \\
			\textbf{mushroom}             & \cellcolor[rgb]{ 1,  .922,  .518}6,5538 ($\pm$1,071)                              & \cellcolor[rgb]{ .992,  .718,  .478}9,0452 ($\pm$1,093) & \cellcolor[rgb]{ .98,  .51,  .439}11,5731 ($\pm$1,193)   & \cellcolor[rgb]{ .996,  .816,  .498}7,872 ($\pm$0,92)    & \cellcolor[rgb]{ .988,  .659,  .471}9,7527 ($\pm$1,083)  & \cellcolor[rgb]{ .98,  .557,  .451}10,9785 ($\pm$1,108)  & \cellcolor[rgb]{ .973,  .412,  .42}12,7097 ($\pm$1,478)  \\
			\textbf{parkinsons}           & \cellcolor[rgb]{ .875,  .882,  .51}6,472 ($\pm$2,423)                             & \cellcolor[rgb]{ .996,  .843,  .506}8,3161 ($\pm$1,644) & \cellcolor[rgb]{ 1,  .898,  .514}7,7968 ($\pm$1,719)     & \cellcolor[rgb]{ .996,  .827,  .502}8,4892 ($\pm$1,901)  & \cellcolor[rgb]{ .98,  .494,  .435}11,7516 ($\pm$1,155)  & \cellcolor[rgb]{ .973,  .412,  .42}12,5419 ($\pm$1,351)  & \cellcolor[rgb]{ .984,  .584,  .455}10,8742 ($\pm$1,317) \\
			\textbf{student\_performance} & \cellcolor[rgb]{ .514,  .78,  .486}3,4194 ($\pm$2,006)                            & \cellcolor[rgb]{ 1,  .902,  .514}6,9333 ($\pm$2,44)     & \cellcolor[rgb]{ 1,  .886,  .514}7,1032 ($\pm$1,989)     & \cellcolor[rgb]{ .98,  .537,  .443}11,0624 ($\pm$1,067)  & \cellcolor[rgb]{ .988,  .918,  .514}6,6366 ($\pm$2,023)  & \cellcolor[rgb]{ 1,  .922,  .518}6,7011 ($\pm$2,242)     & \cellcolor[rgb]{ .996,  .804,  .498}8,0323 ($\pm$1,935)  \\
			\textbf{wine\_quality}        & \cellcolor[rgb]{ 1,  .922,  .518}6,0011 ($\pm$2,404)                              & \cellcolor[rgb]{ .988,  .647,  .467}9,5935 ($\pm$1,494) & \cellcolor[rgb]{ .984,  .588,  .455}10,3387 ($\pm$1,62)  & \cellcolor[rgb]{ .98,  .525,  .443}11,1602 ($\pm$1,773)  & \cellcolor[rgb]{ .992,  .722,  .482}8,6344 ($\pm$1,18)   & \cellcolor[rgb]{ .988,  .651,  .467}9,5269 ($\pm$1,341)  & \cellcolor[rgb]{ .973,  .412,  .42}12,5903 ($\pm$1,352)  \\
			\midrule
			\textbf{avg rank}             & \cellcolor[rgb]{ 1,  .922,  .518}6,2727 ($\pm$3,004)                              & \cellcolor[rgb]{ .992,  .776,  .49}7,7855 ($\pm$2,271)  & \cellcolor[rgb]{ .988,  .639,  .467}9,1522 ($\pm$2,48)   & \cellcolor[rgb]{ .984,  .612,  .459}9,4451 ($\pm$2,75)   & \cellcolor[rgb]{ .984,  .592,  .455}9,6445 ($\pm$2,214)  & \cellcolor[rgb]{ .98,  .529,  .443}10,2877 ($\pm$2,346)  & \cellcolor[rgb]{ .973,  .412,  .42}11,4538 ($\pm$2,354)  \\
			\midrule
			\textbf{normalised avg rank}  & \cellcolor[rgb]{ 1,  .922,  .518}7                                                & \cellcolor[rgb]{ .996,  .839,  .502}8                   & \cellcolor[rgb]{ .992,  .753,  .486}9                    & \cellcolor[rgb]{ .988,  .667,  .471}10                   & \cellcolor[rgb]{ .984,  .584,  .455}11                   & \cellcolor[rgb]{ .98,  .498,  .439}12                    & \cellcolor[rgb]{ .973,  .412,  .42}13                    \\
			\cmidrule{3-3}\end{tabular}%
	}
\end{table}%
